\documentclass[12pt]{jarticle} % Japanese
%\documentclass[12pt]{article} % English
% if there are problems in the above regarding fonts, use this
% \documentclass[UTF8]{ctexart}



%package
\usepackage{amssymb, amsmath, newtxmath}
\usepackage{cite}
\usepackage[utf8]{inputenc}
%\usepackage{utf}
\usepackage{naist-jmthesis} %Japanese
%\usepackage{naist-mthesis} %English
\usepackage[dvipdfmx]{graphicx}
\usepackage[dvipdfmx]{hyperref}
\usepackage{pxjahyper} %Required pxjahyper.sty
\usepackage[dvipdfmx]{xcolor}
\usepackage{pxjahyper} %TOC文字化け対策
\usepackage{booktabs}
\usepackage{here}



%definition
\definecolor{purple}{RGB}{98, 114, 164}
\hypersetup{
 colorlinks=true,
 linkcolor=black,
 citecolor=purple,
 urlcolor=black,
 filecolor=purple,
 anchorcolor=purple,
 pdfborder={0, 0, 1},
 linktoc=all
}
\renewcommand\thefootnote{\textcolor{purple}{\Roman{footnote}}}


% Page style
\pagestyle{final}       % Camera-Ready
%\pagestyle{draft}      % Draft
\lang{Japanese} % Japanese
%\lang{English} % English
% Student Number
\studentnumber{1811147}
\doctitle{\mastersthesis}% 修士論文
\major{\engineering}     % 工学



% 日本語題目 (in LaTeX)
\title{トンネリング抑止を目的とした\\分散ハッシュテーブルを利用したDNSに関する研究}
% 日本語題目 (in plain text)
%   注: (in LaTeX)と同じ場合は指定する必要なし。
%       この情報は修士論文/課題研究には現れませんが、管理のために必要です。
%\ptitle{再帰問い合わせ名前解決へのハッシュ関数を用いたDNS Exfiltration緩和策の提案}



% 英語題目 (in LaTeX)
%\etitle{Proposal for Mitigation of DNS Exfiltraion using Hash Function to Recursive Name Resolution}
\etitle{A Study of Domain Name System using Distributed Hash Table \\for Tunneling Deterrence}
% 英語題目 (in plain text)
%   注: (in LaTeX)と同じ場合は指定する必要なし。
%       この情報は修士論文/課題研究には現れませんが、管理のために必要です。
%\eptitle{Theoretical Studies on Low-Speed Calculation Algorithms of pi \\
%Utilizing the Sun and the Moon}
%\eptitle{Proposal for Mitigation of DNS Exfiltraion using Hash Function to Recursive Name Resolution}



% 日本語氏名 (in LaTeX)
%   （姓と名の間に空白を入れて下さい）
\author{高須賀 昌烈}
%\pauthor{}
%   （first name, last name の順に記入し、先頭文字のみを大文字にする。）
\eauthor{Shoretsu Takasuka}
% 別の例: \eauthor{Kurt G\"{o}del}
%\epauthor{}



% 論文提出年月日
\syear{2020}
\smonth{1}
\sday{28}



% 専攻の選択
%\department{\infproc}  % 情報処理学
%\department{\infsys}    % 情報システム学
%\department{\bioinf}   % 情報生命科学
\department{\infsci}    % 情報科学



% 審査委員（日本語）
%   （姓と名、名と称号の間に空白を入れて下さい）
%５人以上の場合，５人目以降は\addcmembers を使って宣言する。
%最大で合わせて８人まで宣言可能。
%主指導教員、副指導教員を明記する。両指導教員以外は委員。
%学外審査委員は、大学名を明記する
% ４人の場合
\cmembers{門林 雄基 教授}{（主指導教員）}
         {笠原 正治 教授}{（副指導教員）}
         {林 優一 教授}{（副指導教員）}
         {妙中 雄三 准教授}{（副指導教員）}
% ３人の場合
%\cmembers{○○ ○○ 教授}{（主指導教員）}
%         {○○ ○○ 教授}{（副指導教員）}
%         {○○ ○○ 准教授}{（副指導教員）}
%         {}{}
% ２人の場合
%\cmembers{○○ ○○ 教授}{（主指導教員）}
%         {○○ ○○ 教授}{（副指導教員）}
%          {}{}
%          {}{}



% 審査委員（英語）
%     （first name, last name の順に記入し、先頭文字のみを大文字にする。
%       first name と last name の間に空白、
%       last name と 称号の間にカンマと空白を入れて下さい。）
% ５人以上の場合，５人目以降は\eaddcmembers を使って宣言する
% Supervisor, Co-supervisor, and Member must be specified.
% ４人の場合
\ecmembers{Professor Youki Kadobayashi}{(Supervisor)}
          {Professor Shoji Kasahara}{(Co-supervisor)}
          {Professor Yu-ichi Hayashi}{(Co-supervisor)}
          {Associate Professor Yuzo Taenaka}{(Co-supervisor)}
% ３人の場合
%\ecmembers{Professor xx xx}{(Supervisor)}
%          {Professor xx xx}{(Co-supervisor)}
%          {Associate Professor xx xx}{(Co-supervisor)}
%          {}{}
% ２人の場合
% \ecmembers{Professor xx xx}{(Supervisor)}
%           {Professor xx xx}{(Co-supervisor)}
%           {}{}
%           {}{}



% ===================キーワード===================
\keywords{ドメインネームシステム，DNSトンネリング，分散ハッシュテーブル，P2Pネットワーク}
% キーワード５〜６個 (in plain text)
%   注: (in LaTeX)と同じ場合は記入する必要なし。
%       この情報は修士論文/課題研究には現れませんが、管理のために必要です。
%\pkeywords{pi, 天文学, 数学, 計算機, アルゴリズム}
%\pkeywords{DNS Exfiltration, 秘匿通信，ハッシュ関数，再帰問い合わせ}
% 5 or 6 Keywords (in LaTeX)
%\ekeywords{$\pi$, astronomy, mathematics, computer, algorithm}



% ===================Keyword===================
\ekeywords{Domain Name System(DNS), DNS Tunneling, Distributed Hash Table(DHT), P2P Network}
% 5 or 6 Keywords (in plain text)
%   注: (in LaTeX)と同じ場合は記入する必要なし。
%       この情報は修士論文/課題研究には現れませんが、管理のために必要です。
%\epkeywords{pi, astronomy, mathematics, computer, algorithm}
%\epkeywords{DNS Exfiltration, Covert Channel, Hash Function, Recursive Name Resolution}



% ===================内容梗概===================
\abstract{
% ネットワークプロトコルスタックの一つとして，IPアドレスとドメイン名を対応づけるDNSがある．
% 名前解決の機能を提供するDNSだが，情報流出として機能することが
}
%   注: 行の先頭が\\で始まらないようにすること。
%   注: (in LaTeX)と同じ場合は記入する必要なし。
%       この情報は修士論文/課題研究には現れませんが、管理のために必要です。
%       改行する箇所には空白行を入れる。
%       行の先頭が\\で始まらないようにすること。
%\pabstract{
%}
% Abstract (in LaTeX)
%  注: 　行の先頭が\\で始まらないようにすること。



% ===================Abstruct===================
\eabstract{
}
% Abstract (in plain text)
%   注: (in LaTeX)と同じ場合は記入する必要なし。
%       この情報は修士論文/課題研究には現れませんが、管理のために必要です。
%       改行する箇所には空白行を入れる。
%       行の先頭が\\で始まらないようにすること。
%\epabstract{
%The calculation of pi has been paid much attention since human beings
%appeared on the earth.
%This thesis presents novel low-speed algorithms to calculate
%pi utilizing the sun and the moon.
%This is a sample abstract. This is a sample abstract.
%}



% ===================表紙===================
\begin{document}
\titlepage
\cmemberspage
\firstabstract
\secondabstract



% ===================目次===================
\toc
\newpage
\listoffigures
%\newpage
\listoftables



% ===================本文===================
\newpage
\pagenumbering{arabic}

\include{section/introduction}
\include{section/preliminaries}
\include{section/related_works}
\include{section/proposed_method}
\include{section/evaluation}
\include{section/discussion}
\include{section/conclusion}



% ===================謝辞===================
\newpage
\acknowledgements
ご指導ご鞭撻賜りありがとうございました．




% ===================参考文献===================
% ここでは \reference を使って、自分でリストを作るか、BibTeX を使って
% リストをつくって下さい。この例では BibTeX を作るような形式になってい
% ます。
\newpage
%\reference
%\bibliographystyle{plain}
\begin{thebibliography} {25}\small
 \bibitem{rfc1034} P.V. Mockapetris. ``Domain names - concepts and facilities. RFC 1034 (INTERNET STANDARD)," November 1987.
 \bibitem{rfc1035} P.V. Mockapetris. ``Domain names - implementation and specification. RFC 1035 (INTERNET STANDARD)," November 1987.
 \bibitem{rfc4033} R. Arends, R. Austein, M. Larson, D. Massey, S. Rose. ``DNS Security Introduction and Requirements, " March 2005. Updated by RFCs 6014, 6840.
 \bibitem{rfc4648} S. Josefsson. ``The Base16, Base32, and Base64 Data Encodings, " October 2006. Updated by RFC 3548.
 \bibitem{covertchannel} ICANN, ``What Is an Internet Covert Channel?," August 2016. \href{https://www.icann.org/news/blog/what-is-an-internet-covert-channel}{https://www.icann\\.org/news/blog/what-is-an-internet-covert-channel}. (accessed 2019-12-12).
 \bibitem{rfc7626} S. Bortzmeyer. ``DNS Privacy Considerations RFC 7626 (INTERNET STANDARD), " August 2015.
 \bibitem{frameworkpos} KrebsonSecurity. ``Deconstructing the 2014 Sally Beauty Breach," May 2015. \href{https://krebsonsecurity.com/2015/05/deconstructing-the-2014-sally-beauty-breach/}{https://krebsonsecurity.com/2015/05/deconstructing-the-2014-sally-beauty-breach/}. (accessd 2019-11-30).
 \bibitem{bondupdater} IronNet. ``Chirp of the PoisonFrog," February 2019. \href{https://ironnet.com/blog/chirp-of-the-poisonfrog/}{https://ironnet.com/blog/ch\\irp-of-the-poisonfrog/}. (accessd 2019-11-30).
 \bibitem{bernhardpos} Nick Hoffman. ``BernhardPOS," July 2015. \href{https://securitykitten.github.io/2015/07/14/bernhardpos.html}{https://securitykitten.github.io/2015/\\07/14/bernhardpos.html}. (accessd 2019-11-30).
 \bibitem{multigrainpos} Fireeye. ``MULTIGRAIN – Point of Sale Attackers Make an Unhealthy Addition to the Pantry," April 2016. \href{https://www.fieeye.com/blog/threat-research/2016/04/multigrain\_pointo.html}{https://www.fieeye.com/blog/threat-research/2016/04/multigrain\_pointo.html}. (accessd 2019-11-30).
 \bibitem{pisloader} Palo alto Networks. ``New Wekby Attacks Use DNS Requests As Command and Control Mechanism," May 2016. \href{https://unit42.paloaltonetworks.com/unit42-new-wekby-attacks-use-dns-requests-as-command-and-control-mechanism/}{https://unit42.paloaltonetworks.com/unit42-new-wekby-attacks-use-dns-requests-as-command-and-control-mechanism/}. (accessd 2019-11-30).
 \bibitem{denis} Kaspersky. ``Use of DNS Tunneling for C\&C Communications," April 2017. \href{https://securelist.com/use-of-dns-tunneling-for-cc-communications/78203/}{https://securelist.com/use-of-dns-tunneling-for-cc-communications/78203/}. (accessd 2019-11-30).
 \bibitem{dnsmessenger} CISCO Talos. ``Spoofed SEC Emails Distribute Evolved DNSMessenger," October 2017. \href{https://blog.talosintelligence.com/2017/10/dnsmessenger-sec-campaign.html}{https://blog.talosintelligence.com/2017/10/dnsmessenger-sec-campaign.html}. (accessd 2019-11-30).
 \bibitem{udpos} Cylance. ``Threat Spotlight: Inside UDPoS Malware," Febrary 27 2018. \href{https://threatvector.cylance.com/en\_us/home/threat-spotlight-inside-udpos-malware.html}{https://threatvector.cylance.com/en\_us/home/threat-spotlight-inside-udpos-malware.html}. (accessd 2019-11-30).
 \bibitem{born} K. Born and D. Gustafson, ``NgViz: detecting DNS tunnels through n-gram visualization and quantitative analysis," Proceedings of the Sixth Annual Workshop on Cyber Security and Information Intelligence Research, Oak Ridge, Tennessee, 2010, pp. 1-4.
 \bibitem{cheng} Cheng Qi, Xiaojun Chen, Cui Xu, Jinqiao Shi, Peipeng Liu, ``A Bigram based Real Time DNS Tunnel Detection Approach," Procedia Computer Science, Volume 17, 2013, Pages 852-860.
 \bibitem{liu} J. Liu, S. Li, Y. Zhang, J. Xiao, P. Chang and C. Peng, ``Detecting DNS Tunnel through Binary-Classification Based on Behavior Features," 2017 IEEE Trustcom/BigDataSE/ICESS, Sydney, NSW, 2017, pp. 339-346.
 \bibitem{asaf} Asaf Nadler, Avi Aminov, Asaf Shabtai, ``Detection of malicious and low throughput data exfiltration over the DNS protocol," Computers \& Security, Volume 80, 2019, Pages 36-53.
 \bibitem{steadman} J. Steadman and S. Scott-Hayward, ``DNSxD: Detecting Data Exfiltration Over DNS," 2018 IEEE Conference on Network Function Virtualization and Software Defined Networks (NFV-SDN), Verona, Italy, 2018, pp. 1-6.
 \bibitem{jawad} J. Ahmed, H. H. Gharakheili, Q. Raza, C. Russell and V. Sivaraman, ``Monitoring Enterprise DNS Queries for Detecting Data Exfiltration from Internal Hosts," in IEEE Transactions on Network and Service Management.
 \bibitem{ozymandns} ``OzymanDNS - Tunneling SSH over DNS," \href{https://room362.com/post/2009/2009310ozymandns-tunneling-ssh-over-dns-html/}{https://room362.com/post/2009/2009310ozymandns-tunneling-ssh-over-dns-html/}, (accessed 2019-11-20).
 \bibitem{iodine} ``iodine," \href{http://code.kryo.se/iodine/}{http://code.kryo.se/iodine/}, (accessed 2019-11-20).
 \bibitem{dnscat2} ``DNScat2," \href{https://github.com/iagox86/dnscat2}{https://github.com/iagox86/dnscat2}, (accessed 2019-11-20).
 \bibitem{tcp-over-dns} ``TCP-over-DNS, " \href{http://analogbit.com/software/tcp-over-dns/}{http://analogbit.com/software/tcp-over-dns/}
 \bibitem{dnscat} ``dnscat, " \href{https://wiki.skullsecurity.org/Dnscat}{https://wiki.skullsecurity.org/Dnscat}
 \bibitem{denise} ``DeNiSe, " \href{https://github.com/mdornseif/DeNiSe}{https://github.com/mdornseif/DeNiSe}
 \bibitem{dns-shell} ``DNS-shell, " \href{https://github.com/sensepost/DNS-Shell}{https://github.com/sensepost/DNS-Shell}
 \bibitem{dnsbotnet} ``DNSBotnet, " \href{https://github.com/magisterquis/dnsbotnet}{https://github.com/magisterquis/dnsbotnet}
 \bibitem{dnscapy} ``DNScapy, " \href{https://github.com/FedericoCeratto/dnscapy}{https://github.com/FedericoCeratto/dnscapy}
 \bibitem{dohtunnel} ``dohtunnel, " \href{https://github.com/jansect/dohtunnel/blob/master/doh/doh.go}{https://github.com/jansect/dohtunnel/blob/master/doh/doh.go}
 \bibitem{godoh} ``goDoH, " \href{https://github.com/sensepost/goDoH}{https://github.com/sensepost/goDoH}
 \bibitem{dohc2} ``DoHC2, " \href{https://github.com/SpiderLabs/DoHC2}{https://github.com/SpiderLabs/DoHC2}
 \bibitem{magictunnelandroid} ``magicTunnelAndroid, " \href{https://github.com/MagicTunnel/MagicTunnelAndroid}{https://github.com/MagicTunnel/MagicTunnelAndroid}
 \bibitem{Ramasubramanian} Ramasubramanian, Venugopalan and Sirer, Emin G\"{u}n, ``The Design and Implementation of a next Generation Name Service for the Internet, " Association for Computing Machinery, NY, USA, SIGCOMM Comput. Commun. Rev, number 4 Volume 34, pp.331–342.
 \bibitem{Danielis} P. Danielis, V. Altmann, J. Skodzik, T. Wegner, A. Koerner and D. Timmermann, "P-DONAS: A P2P-Based Domain Name System in Access Networks," in ACM Transactions on Internet Technology (TOIT), vol. 15, no. 3, pp. 1-21, September 2015.
 \bibitem{namecoin} ``Namecoin, " \href{https://www.namecoin.org/}{https://www.namecoin.org/}, (accessed 2019-12-30)
 \bibitem{nmap} ``Bugtraq mailing list archives DNS Tunnel - through bastion hosts, " \href{https://seclists.org/bugtraq/1998/Apr/79}{https://seclists.org/bugtraq/1998/Apr/79}, (accessed 2019-1-4)
\end{thebibliography}
\bibliography{mthesis}




% ===================付録===================
\appendix

\section{発表リスト(国内研究会)}
%\subsection{国内研究会}
\begin{enumerate}
 \item \underline{高須賀 昌烈}, 妙中 雄三, 門林 雄基, ``非実在ドメインに対するネガティブキャッシュの拡張と再帰問い合わせハッシュ化の提案", 電子情報通信学会 情報ネットワーク研究会, 2019-10-ICTSSL-IN, 2019年10月.
\end{enumerate}
%\label{omake1}
%これはおまけです。これはおまけです。これはおまけです。これはおまけです。
%\begin{figure}
%\centerline{これはおまけの図です。}
%\caption{おまけの図}
%\end{figure}
%\section{おまけその２}
%これもおまけです。これもおまけです。これもおまけです。これもおまけです。



\end{document}
